---
title: "news-data-eda"
author: "Rachdyan"
output: github_document
always_allow_html: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

We want to create a wordcloud and a bar chart that shows the most frequent word in the news headline

First, load the needed libraries

```{r libraries, echo = T, message = F, warning = F}
library(ggplot2)
library(wordcloud)
library(RColorBrewer)
library(tm)
library(xlsx)
library(readxl)
library(dplyr)
library(tidyquant)
```


## Load The Data


```{r load_data, echo=TRUE}
# Load the data
news_data <- read_xlsx("./data/news_data.xlsx")

# Get the news headline
headlines <- news_data$headline

# Get a look of the data
head(headlines)
```

## Prepare the Data

Before creating the visualizations, we have to prepare the data

```{r prepare_data, echo=T, warning = F}

# Remove "gold" word from the headline daat
headlines <- gsub("gold", "", headlines)

# Make a Corpus
headlines_docs <- Corpus(VectorSource(headlines))

# Remove Number, Punctuation, Whitespace
headlines_docs <- headlines_docs %>%
  tm_map(removeNumbers) %>%
  tm_map(removePunctuation) %>%
  tm_map(stripWhitespace)

# Transform into lowercase
headlines_docs <- tm_map(headlines_docs, content_transformer(tolower))

# Remove stop words
headlines_docs <- tm_map(headlines_docs, removeWords, stopwords("english"))

# Create a Term document matrix
dtm <- TermDocumentMatrix(headlines_docs) 
matrix <- as.matrix(dtm) 
words <- sort(rowSums(matrix),decreasing=TRUE) 

# Create a data frame containing words and the frequency
headlines_df <- data.frame(word = names(words),freq=words)

# View the Data Frame
head(headlines_df)
```

## Bar Chart

Create a bar chart of top 15 words in the headlines

```{r bar_chart, echo=T}

headlines_df %>% top_n(15) %>% ggplot(aes(x = reorder(word, freq), y = freq, label = freq)) + 
  geom_bar(stat = "identity", position = "dodge", fill = "#2C3E50") +  
  geom_text(hjust = 1.2, color = "#F8F7F3", fontface = "bold") + 
  labs(y="Frequency", 
       x="",
       title = "Most Frequent Word in the News Headline") +
  coord_flip() + 
  theme_tq()
```

The most frequent words used in the headlines are 'dollar', followed by 'fed', 'yields', 'gains', and 'data'

## Word Cloud

Create a wordcloud

```{r word_cloud, echo=T}

set.seed(1313)
wordcloud(words = headlines_df$word, freq = headlines_df$freq, min.freq = 1, 
          max.words=200, random.order=FALSE, 
          rot.per=0.25, 
          colors=brewer.pal(8, "Dark2"))
```